---
title: "Database Space"
author: "John Pertell"
output: 
  flexdashboard::flex_dashboard:
  
params:
  server1: "PERTELLSQL1"
  server2: "PERTELLSQL2"
  server3: "PERTELLSQL3"
  server4: "PERTELLSQL4"
  db1: 'mis_db'
  db2: 'darwin_db'
  db3: 'dialysis_db'
---

# Introduction {.sidebar}

```{r, include = FALSE}
library(RODBC)
library(dplyr)
library(ggplot2)
library(scales)
library(dygraphs)
library(xts)
library(quantmod)
library(tidyr)
library(zoo)

myConn <- odbcDriverConnect("driver={SQL Server};
                            server=PERTELL03;
                            database=DemoDB;
                            Trusted Connection=true")

db_Size <- sqlFetch(myConn, "DBStats")

close(myConn)

db_filtered <- db_Size %>% filter(Servername %in% c('PERTELLSQL1', 'PERTELLSQL2', 'PERTELLSQL3', 'PERTELLSQL4'),
                                  DBName %in% c('mis_db', 'darwin_db','dialysis_db'),
                                  RunDate >= as.POSIXct('2015-08-22')) %>%
  select(Servername, RunDate, DBName, Name, TotalSize, UsedSpace, FreeSpace) 

db_filtered$UsedSpace <- (db_filtered$UsedSpace / 1024) / 1024
```

This report examines the space usage on four SQL instances: 

- `r params$server1` 
- `r params$server2` 
- `r params$server3` 
- `r params$server4` 

It is written in [R Markdown](http://rmarkdown.rstudio.com), an authoring format that enables easy creation of dynamic documents, presentations, and reports from R. R Markdown combines the core syntax of **markdown** (an easy to write plain text format) with embedded **R** code chunks that are run so their output can be included in the final document.

The data is for the 3 largest databases:

- `r params$db1`
- `r params$db2`
- `r params$db3`

# `r params$server1`

### `r params$db1` 
```{r echo = FALSE}
db_plot <- db_filtered %>% filter(Servername == params$server1, DBName == params$db1) %>% 
                           select(RunDate, Name, UsedSpace) %>%
                           spread(Name, UsedSpace)  

db_plot2 <- read.zoo(db_plot, order.by = db_plot$RunDate)
dygraph(db_plot2) %>% 
  dyAxis('y', label = 'Used Space (GB)', valueRange = c(0, 220)) %>% 
  dyOptions(fillGraph = TRUE, fillAlpha = 0.4) %>% 
  dyLegend(width = 600) %>%
  dyRangeSelector()
```

### `r params$db2` 
```{r echo = FALSE}
db_plot <- db_filtered %>% filter(Servername == params$server1, DBName == params$db2) %>% 
                           select(RunDate, Name, UsedSpace) %>%
                           spread(Name, UsedSpace)  

db_plot2 <- read.zoo(db_plot, order.by = db_plot$RunDate)
dygraph(db_plot2) %>% 
  dyAxis('y', label = 'Used Space (GB)', valueRange = c(0, 120)) %>% 
  dyOptions(fillGraph = TRUE, fillAlpha = 0.4) %>% 
  dyLegend(width = 600) %>%
  dyRangeSelector()
```

### `r params$db3` 
```{r echo = FALSE}
db_plot <- db_filtered %>% filter(Servername == params$server1, DBName == params$db3) %>% 
                           select(RunDate, Name, UsedSpace) %>%
                           spread(Name, UsedSpace)  

db_plot2 <- read.zoo(db_plot, order.by = db_plot$RunDate)
dygraph(db_plot2) %>% 
  dyAxis('y', label = 'Used Space (GB)', valueRange = c(0, 140)) %>% 
  dyOptions(fillGraph = TRUE, fillAlpha = 0.4) %>% 
  dyLegend(width = 600) %>%
  dyRangeSelector()
```


# `r params$server2`

### `r params$db1` 
```{r echo = FALSE}
db_plot <- db_filtered %>% filter(Servername == params$server2, DBName == params$db1) %>% 
                           select(RunDate, Name, UsedSpace) %>%
                           spread(Name, UsedSpace)  

db_plot2 <- read.zoo(db_plot, order.by = db_plot$RunDate)
dygraph(db_plot2) %>% 
  dyAxis('y', label = 'Used Space (GB)', valueRange = c(0, 220)) %>% 
  dyOptions(fillGraph = TRUE, fillAlpha = 0.4) %>% 
  dyLegend(width = 600) %>%
  dyRangeSelector()
```

### `r params$db2` 
```{r echo = FALSE}
db_plot <- db_filtered %>% filter(Servername == params$server2, DBName == params$db2) %>% 
                           select(RunDate, Name, UsedSpace) %>%
                           spread(Name, UsedSpace)  

db_plot2 <- read.zoo(db_plot, order.by = db_plot$RunDate)
dygraph(db_plot2) %>% 
  dyAxis('y', label = 'Used Space (GB)', valueRange = c(0, 120)) %>% 
  dyOptions(fillGraph = TRUE, fillAlpha = 0.4) %>% 
  dyLegend(width = 600) %>%
  dyRangeSelector()
```


### `r params$db3` 

```{r echo = FALSE}
db_plot <- db_filtered %>% filter(Servername == params$server2, DBName == params$db3) %>% 
                           select(RunDate, Name, UsedSpace) %>%
                           spread(Name, UsedSpace)  

db_plot2 <- read.zoo(db_plot, order.by = db_plot$RunDate)
dygraph(db_plot2) %>% 
  dyAxis('y', label = 'Used Space (GB)', valueRange = c(0, 140)) %>% 
  dyOptions(fillGraph = TRUE, fillAlpha = 0.4) %>% 
  dyLegend(width = 600) %>%
  dyRangeSelector()
```


# `r params$server3`

### `r params$db1` 
```{r echo = FALSE}
db_plot <- db_filtered %>% filter(Servername == params$server3, DBName == params$db1) %>% 
                           select(RunDate, Name, UsedSpace) %>%
                           spread(Name, UsedSpace)  

db_plot2 <- read.zoo(db_plot, order.by = db_plot$RunDate)
dygraph(db_plot2) %>% 
  dyAxis('y', label = 'Used Space (GB)', valueRange = c(0, 220)) %>% 
  dyOptions(fillGraph = TRUE, fillAlpha = 0.4) %>% 
  dyLegend(width = 600) %>%
  dyRangeSelector()
```

### `r params$db2` 
```{r echo = FALSE}
db_plot <- db_filtered %>% filter(Servername == params$server3, DBName == params$db2) %>% 
                           select(RunDate, Name, UsedSpace) %>%
                           spread(Name, UsedSpace)  

db_plot2 <- read.zoo(db_plot, order.by = db_plot$RunDate)
dygraph(db_plot2) %>% 
  dyAxis('y', label = 'Used Space (GB)', valueRange = c(0, 120)) %>% 
  dyOptions(fillGraph = TRUE, fillAlpha = 0.4) %>% 
  dyLegend(width = 600) %>%
  dyRangeSelector()
```

### `r params$db3` 
```{r echo = FALSE}
db_plot <- db_filtered %>% filter(Servername == params$server3, DBName == params$db3) %>% 
                           select(RunDate, Name, UsedSpace) %>%
                           spread(Name, UsedSpace)  

db_plot2 <- read.zoo(db_plot, order.by = db_plot$RunDate)
dygraph(db_plot2) %>% 
  dyAxis('y', label = 'Used Space (GB)', valueRange = c(0, 140)) %>% 
  dyOptions(fillGraph = TRUE, fillAlpha = 0.4) %>% 
  dyLegend(width = 600) %>%
  dyRangeSelector()
```


# `r params$server4`

### `r params$db1` 
```{r echo = FALSE}
db_plot <- db_filtered %>% filter(Servername == params$server4, DBName == params$db1) %>% 
                           select(RunDate, Name, UsedSpace) %>%
                           spread(Name, UsedSpace)  

db_plot2 <- read.zoo(db_plot, order.by = db_plot$RunDate)
dygraph(db_plot2) %>% 
  dyAxis('y', label = 'Used Space (GB)', valueRange = c(0, 220)) %>% 
  dyOptions(fillGraph = TRUE, fillAlpha = 0.4) %>% 
  dyLegend(width = 600) %>%
  dyRangeSelector()
```

### `r params$db2` 
```{r echo = FALSE}
db_plot <- db_filtered %>% filter(Servername == params$server4, DBName == params$db2) %>% 
                           select(RunDate, Name, UsedSpace) %>%
                           spread(Name, UsedSpace)  

db_plot2 <- read.zoo(db_plot, order.by = db_plot$RunDate)
dygraph(db_plot2) %>% 
  dyAxis('y', label = 'Used Space (GB)', valueRange = c(0, 120)) %>% 
  dyOptions(fillGraph = TRUE, fillAlpha = 0.4) %>% 
  dyLegend(width = 600) %>%
  dyRangeSelector()
```

### `r params$db3` 
```{r echo = FALSE}
db_plot <- db_filtered %>% filter(Servername == params$server4, DBName == params$db3) %>% 
                           select(RunDate, Name, UsedSpace) %>%
                           spread(Name, UsedSpace)  

db_plot2 <- read.zoo(db_plot, order.by = db_plot$RunDate)
dygraph(db_plot2) %>% 
  dyAxis('y', label = 'Used Space (GB)', valueRange = c(0, 140)) %>% 
  dyOptions(fillGraph = TRUE, fillAlpha = 0.4) %>% 
  dyLegend(width = 600) %>%
  dyRangeSelector()
```
